\subsection{Relation Properties}
\label{sec:relation_properties_experiment}

\input{content/hypothesis_evaluation/tables/test_set_explanations}
\input{content/hypothesis_evaluation/tables/rel_properties_dataset_stats}
%\input{content/hypothesis_evaluation/tables/relation_properties_folder/icews14_original_timestamps}
%\input{content/hypothesis_evaluation/tables/relation_properties_folder/wikidata12k_original_timestamps}
%\input{content/hypothesis_evaluation/tables/relation_properties_folder/yago11k_original_timestamps}
\input{content/hypothesis_evaluation/tables/relation_properties_folder/hypothesis_3_a}
\input{content/hypothesis_evaluation/tables/relation_properties_folder/hypothesis_3_b}
\input{content/hypothesis_evaluation/tables/relation_properties_folder/hypothesis_3_c}

To evaluate hypothesis \autoref{hyp:relation_properties} the methods have been evaluated on testsets divided into a number of different relation properties. The testsets of each dataset all contain a relation in the query, and predicts on head, tail or timestamp.

In \autoref{tab:relation_property_test_sets} the number of facts in each test set is detailed, as well as the number of types of relations.
For an overview of what each test set contains, see \autoref{tab:test_set_explanations}. There are no relations with the reflexive property in any dataset, and as such test set $T_R$ is empty for all datasets.
%$T_S$ contain all facts that has symmetrical relations, $T_S'$ contain all facts with non-symmetrical relations, $T_A$ contain all facts with anti-symmetrical relations, $T_A'$ contain all facts with non-antisymmetrical relations, $T_I$ contain all facts with inverse relations, $T_I'$ contain all facts with non-inverse relations. $T_R$ is the set of all facts with reflexive relations, but no relations in the datasets has this property, and therefore the set $T_R'$, which contain all facts with non-reflexive relations, contain all facts with known relation. 
The models will only be compared on testsets where there are facts that have a given property and facts that do not have that given property. ICEWS14 is the dataset best suited for analysis of this hypothesis, as there is a higher number of relation types, with more varied relation properties.

All three sub-hypotheses of \autoref{hyp:relation_properties} all refer to specific methods, and what they can and cannot represent. They are all diacronic embedding methods, and they will be compared to the other diachronic embedding methods, as they share the most characteristics with eachother.

To evaluate on \autoref{hyp:relation_property_sym}, we have analyzed and compared the performance of DE-TransE, DE-DistMult, and DE-SimplE, as can be seen in \autoref{tab:hypothesis_3_a_comparison}.
On both dataset ICEWS14 and YAGO, the symmetrical relations seem to be significantly more simple for the embedding methods to represent -- They all achieve a higher performance on the symmetrical dataset than the non-symmetrical dataset. What can also be observed is that DE-TransE has a lower difference in improvement between the symmetrical testsets and the non-symmetrical testsets. In ICEWS14 the performance of DE-TransE is similar across the symmetrical testset as the non-symmetrical. The results are not as strong as we initally anticipated, but it still indicates that DE-TransE performs worse on symmetrical relations than other models do, compared to their performance on non-symmetrical relations, and this indicates that \autoref{hyp:relation_property_sym} is true.

For our analysis of \autoref{hyp:relation_property_antisym}, we have compared the performance of DE-DistMult with DE-TransE and DE-SimplE, as can be seen in \autoref{tab:hypothesis_3_b_comparison}.
As the table shows, there is little that indicates that DE-DistMult is worse at anti-symmetric relations than the other DE models, and the performance of DE-DistMult is almost the same as DE-SimplE. This indicates that DE-DistMult perfoms similarly on anti-symmetrical relations as non-antisymmetrical relations, which indicates that \autoref{hyp:relation_property_antisym} is false, despite the theoretical disadvantage that DE-DistMult has.

Finally, to evaluate \autoref{hyp:relation_property_inv}, we have compared the performance of DE-DistMult with the performance of DE-TransE and DE-SimplE, on an inverse relation testset and a non-inverse relation testset in \autoref{tab:hypothesis_3_c_comparison}. Only ICEWS14 has inverse relations.
The comparison shows that DE-DistMult has higher performance on the inverse testset than the non-inverse testset, but the difference between these two performance results are lower then on other models. The difference is not very significant however, and the performance is overall similar to the performance of DE-SimplE. These results are not sigificant enough to confirm the hypothesis, and therefore the results indicate that \autoref{hyp:relation_property_inv} is false, however this result is only based on a single dataset, and therefore is not very well supported.

Overall these results seem to indicate that \autoref{hyp:relation_properties} is true under some circumstances, which indicate that the real performance of each model can in some cases be predicted by the theoretical limitations of the methods, but the methods will also achieve good results despite it.

\begin{comment}
\autoref{tab:relation_properties_icews14_comparison} contains our findings for the dataset ICEWS14. The expected behaviour for DE-TransE is to have a worse score of symmetrical relations as this model cannot model symmetry, as is outlined in \autoref{tab:overview_of_models}. The results indicate that this is not the case -- DE-TransE has a similar overall score on test set $T_S$ as $T_S'$. Most of the models have a better score on $T_S$ however, which indicates that the symmetrical relations are simply easier to predict on for the models than the non-symmetrical ones.

DE-DistMult is expected to have a worse score for anti-symmetry and inversion. This is also not the case, as the score for anti-symmetry is similar to the score for non-antisymmetrical relations on DE-DistMult on dataset ICEWS14. The score for inverse relations are significantly higher than the score for non-inverse relation.

DE-SimplE is expected to combine the best parts of DE-TransE and DE-DistMult, and achieve similar or better results than the two other methods across relation types. This seems to be the case, as DE-Simple has a higher or similar MRR score than the other DE models on every testset.

TeRo seems to have a significantly higher MRR score on symmetrical and inverse relations, and a similar score on anti-symmetrical ranks. ATiSE follows the same pattern. \missing[Write something about TeRo and ATiSE]

TimePlex has a significantly lower score on symmetrical and inverse relations, and a significantly higher score on anti-symmetrical relations. This is the most unique distribution of best results, and might be related to the category of the model, as TimePlex is the only neural network model tested.

\autoref{tab:relation_properties_wikidata12k_comparison} contains our findings for quality of predictions on WIKIDATA. This dataset only has relations that have anti-symmetrical properties among the properties that we inspect, and therefore the figure contains only those findings. The models overall have similar performance across anti-symmetrical relations, which is only surprising on the DE-DistMult method, as this method is not supposed to be able to model anti-symmetry.

\autoref{tab:relation_properties_yago11k_comparison} contains our findings for the predictions of models on testsets in YAGO. The relation types are not very varied in YAGO, and each relation that is not symmetrical is anti-symmetrical and vice versa. The results illustrate that the symmetrical relations are overall easier for the models to make predictions on than the set of non-symmetrical relations.

Overall, from the findings in these tests it is possible to conclude that hypothesis \autoref{hyp:relation_properties} is false, and there seems to be no correlation between what each model is theoretically able to depict and what the models are able to depict in reality.
\end{comment}

