\subsection{Dataset \& Split Comparisons}
\label{subsec:dataset_split_comparisons}

To support the reliability of our observations, some of the models have been evaluated using different datasets and different splits of the dataset. In \cite{P9}, we discovered that the best performing results on models trained on ICEWS14 was predictions where the tail was the target of the prediction, followed by the head, relation, and then timestamp. To investigate whether this is a coincidence, we created three new splits of ICEWS14, trained some models on these new splits, and checked the quality of predictions on these splits. The same pattern emerged, confirming that the predictions on ICEWS14 follows this expected result on prediction targets.

The same experiment was conducted using the datasets WIKIDATA12k and YAGO11k, also including the original splits of those datasets and three new ones. These datasets and new splits all exhibited a different pattern for prediction targets. The relation prediction is most accurate, followed by the tail, head and then time predictions. This is likely because these two datasets have a significantly lower amount of relation types in the system, and it is therefore more likely to be correct. This indicates that the quality of the predictions are influenced by the target of the prediction together with the dataset.

\input{content/preliminary_experiments/tables/overall_results}
\input{content/preliminary_experiments/tables/split_results}

To see the overall MRR score of the models trained on the original splits see \autoref{tab:overall_results}. For the the overall MRR scores of models trained on the alternative splits, see \autoref{tab:split_results}.
